Ages of Planets and Stars Observed by Kepler

### 2024-04-02 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{prot_teff_Santos19_Santos21_clean0.pdf}
		}
		\vspace{-0.62cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{koi_mean_prot_teff.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Rotation periods for Kepler stars (left) and planets (right)}.
    These periods are from \citet{Santos_2019}
    (\citetalias{Santos_2019}) and \citet{Santos_2021}
    (\citetalias{Santos_2021}).
    The gray models... %TODO FIXME
	}
	\label{fig:prot_vs_teff}
\end{figure*}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{prot_teff_Santos19_Santos21_clean0.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{koi_mean_prot_teff_koi_X_S19S21dquality_keepgrazing.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Rotation periods for Kepler stars (left) and planets (right)}.
    The periods are from \citet{Santos_2019}
    (\citetalias{Santos_2019}) and \citet{Santos_2021}
    (\citetalias{Santos_2021}), and the temperatures are primarily
    from \citet{Berger_2020a_catalog}.
    The gray models are fits from \citet{Bouma_2023} to open clusters;
    stars of the same mass and age can have many possible rotation
    periods, which sets the empirical precision limit of
    rotation-based age dating.
    The stellar sample shows only apparently single stars near the
    main sequence with $\log g$$>$4.2, RUWE$<$1.4, 3800$<$$T_{\rm
    eff}$$<$6200, that are not flagged as eclipsing binaries.
    The planet sample has the same stellar cuts, 
    and shows confirmed and candidate planets from the cumulative KOI table, 
    requiring them to have a MES$>$10.
    Grazing objects ($b$>0.8) include 213 of the planet candidates
    displayed, and 136 of the host stars.
	}
	\label{fig:prot_vs_teff}
\end{figure*}
